\begin{frame}{Related Works: LoRA}
\begin{itemize}
  \item LoRA freezes the pretrained model and trains low-rank matrices in selected layers.
  \item It significantly reduces trainable parameters while preserving strong downstream performance.
  \item A key hyperparameter is the rank \(r\), which is often selected manually.
\end{itemize}

\vspace{8pt}
\begin{block}{Limitation}
Fixed-rank LoRA does not adapt its capacity to the dataset or to training dynamics.
\end{block}
\end{frame}

\begin{frame}{Related Works: AdaLoRA}
\begin{itemize}
  \item AdaLoRA allocates parameter budget adaptively across LoRA modules.
  \item It starts from a larger initial rank and prunes/reallocates rank according to importance.
  \item It improves parameter efficiency compared with fixed-rank LoRA.
\end{itemize}

\vspace{8pt}
\begin{block}{Limitation}
The base target rank, initial rank, dropout, schedule, and target module set are still usually chosen without explicit dataset profiling.
\end{block}
\end{frame}

\begin{frame}{Gap in Existing Methods}
\begin{table}
\centering
\small
\begin{tabular}{lccc}
\toprule
Method & Rank Adaptation & Dataset Profiling & Stability Logging \\
\midrule
Full fine-tuning & -- & -- & -- \\
LoRA & No & No & Optional \\
AdaLoRA & Yes & No & Optional \\
Proposed method & Yes & Yes & Yes \\
\bottomrule
\end{tabular}
\end{table}

\vspace{8pt}
\begin{itemize}
  \item This work focuses on the missing link between dataset statistics and AdaLoRA configuration.
\end{itemize}
\end{frame}
